``Dr.~Tustison (UVA) presentation''

### 2016-07-17 ibm.tex
ENH:  Last minute refinements.

\begin{frame}[fragile]{\texttt{antsMultivariateTemplateConstruction.sh}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsMultivariateTemplateConstruction.sh}

\KeywordTok{Usage}\NormalTok{:}

\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d ImageDimension -o OUTPREFIX }\KeywordTok{<}\NormalTok{other options}\KeywordTok{>} \KeywordTok{<}\NormalTok{images}\KeywordTok{>}

\KeywordTok{Compulsory} \NormalTok{arguments (minimal command line requires SGE cluster, otherwise use -c }\KeywordTok{&} \KeywordTok{-j} \NormalTok{options)}\KeywordTok{:}

     \KeywordTok{-d}\NormalTok{:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)}
   \KeywordTok{ImageDimension}\NormalTok{: 4 (for template generation of time-series data)}

     \KeywordTok{-o}\NormalTok{:  OUTPREFIX}\KeywordTok{;} \KeywordTok{A} \NormalTok{prefix that is prepended to all output files.}

\KeywordTok{<images>}  \NormalTok{List of images in the current directory, eg *_t1.nii.gz. Should be at the end}
          \KeywordTok{of} \NormalTok{the command.  Optionally, one can specify a .csv or .txt file where each}
          \KeywordTok{line} \NormalTok{is the location of the input image.  One can also specify more than}
          \KeywordTok{one} \NormalTok{file for each image for multi-modal template construction (e.g. t1 and t2)}\KeywordTok{.}
          \KeywordTok{For} \NormalTok{the multi-modal case, the templates will be consecutively numbered (e.g.}
          \KeywordTok{template0.nii.gz}\NormalTok{, template1.nii.gz, ...)}\KeywordTok{.}

\KeywordTok{NB}\NormalTok{: All images to be added to the template should be in the same directory, and this script}
\KeywordTok{should} \NormalTok{be invoked from that directory.}

\KeywordTok{Optional} \NormalTok{arguments:}

     \KeywordTok{-c}\NormalTok{:  Control for parallel computation (default 1) }\KeywordTok{--} \NormalTok{0 == run serially,  1 == SGE qsub,}
          \KeywordTok{2} \NormalTok{== use PEXEC (localhost), }\KeywordTok{3} \NormalTok{== Apple XGrid, 4 == PBS qsub, 5 == SLURM}

     \KeywordTok{-g}\NormalTok{:  Gradient step size (default 0.25) }\KeywordTok{--} \NormalTok{smaller in magnitude results in more cautious steps}

     \KeywordTok{-i}\NormalTok{:  Iteration limit (default 4) }\KeywordTok{--} \NormalTok{iterations of the template construction (Iteration limit)}\KeywordTok{*NumImages} \NormalTok{registrations.}

     \KeywordTok{-j}\NormalTok{:  Number of cpu cores to use (default 2}\KeywordTok{;} \KeywordTok{--} \NormalTok{requires }\StringTok{"-c 2"}\NormalTok{)}

     \KeywordTok{-k}\NormalTok{:  Number of modalities used to construct the template (default 1)}

     \KeywordTok{-w}\NormalTok{:  Modality weights used in the similarity metric (default = 1) }\KeywordTok{---} \NormalTok{specified as e.g. 1x0.5x0.75}

     \KeywordTok{-m}\NormalTok{:  Max-iterations in each registration}

     \KeywordTok{-n}\NormalTok{:  N4BiasFieldCorrection of moving image (default 1) }\KeywordTok{--} \NormalTok{0 == off, 1 == on}

     \KeywordTok{-p}\NormalTok{:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)}

     \KeywordTok{-r}\NormalTok{:  Do rigid-body registration of inputs before creating template (default 0) }\KeywordTok{--} \NormalTok{0 == off 1 == on. Only useful when}
          \KeywordTok{you} \NormalTok{do not have an initial template}

     \KeywordTok{-s}\NormalTok{:  Type of similarity metric used for registration.}

     \KeywordTok{-t}\NormalTok{:  Type of transformation model used for registration.}

     \KeywordTok{-x}\NormalTok{:  XGrid arguments (e.g., -x }\StringTok{"-p password -h controlhost"}\NormalTok{)}

     \KeywordTok{-y}\NormalTok{:  Update the template with the full affine transform (default 1)}\KeywordTok{.} \KeywordTok{If} \NormalTok{0, the rigid}
          \KeywordTok{component} \NormalTok{of the affine transform will not be used to update the template. If your}
          \KeywordTok{template} \NormalTok{drifts in translation or orientation try -y 0.}

     \KeywordTok{-z}\NormalTok{:  Use this this volume as the target of all inputs. When not used, the script}
          \KeywordTok{will} \NormalTok{create an unbiased starting point by averaging all inputs. Use the full path!}

     \KeywordTok{-b}\NormalTok{:  Boolean for saving iteration output to directories (default = 0)}\KeywordTok{.}

\KeywordTok{Example}\NormalTok{:}

\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz}

\KeywordTok{-} \NormalTok{In this example 30x50x20 iterations per registration are used for template creation (that is the default)}
\KeywordTok{-} \NormalTok{Greedy-SyN and CC are the metrics to guide the mapping.}
\KeywordTok{-} \NormalTok{Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional)}\KeywordTok{.}
\KeywordTok{-} \NormalTok{The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) }\KeywordTok{to} \NormalTok{distribute the computation.}
\KeywordTok{-} \NormalTok{if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.}

\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{ANTS} \NormalTok{was created by:}
\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{Brian} \NormalTok{B. Avants, Nick Tustison and Gang Song}
\KeywordTok{Penn} \NormalTok{Image Computing And Science Laboratory}
\KeywordTok{University} \NormalTok{of Pennsylvania}

\KeywordTok{Please} \NormalTok{reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script}
\KeywordTok{in} \KeywordTok{your} \NormalTok{studies. A reproducible evaluation of ANTs similarity metric performance in}
\KeywordTok{brain} \NormalTok{image registration:}

\KeywordTok{*} \NormalTok{Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.}

\KeywordTok{Also} \NormalTok{see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.}

\KeywordTok{The} \NormalTok{script has been updated and improved since this publication.}

\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{script} \NormalTok{adapted by N.M. van Strien, http://www.mri-tutorial.com }\KeywordTok{|} \KeywordTok{NTNU} \NormalTok{MR-Center}
\KeywordTok{multivariate} \NormalTok{template adaption by Nick Tustison}
\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{Apple} \NormalTok{XGrid support by Craig Stark}
\KeywordTok{--------------------------------------------------------------------------------------}
\end{Highlighting}
\end{Shaded}

@@

\begin{frame}[fragile]{\texttt{N4BiasFieldCorrection}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{N4BiasFieldCorrection} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{N4BiasFieldCorrection}
          \KeywordTok{N4} \NormalTok{is a variant of the popular N3 (nonparameteric nonuniform normalization)}
          \KeywordTok{retrospective} \NormalTok{bias correction algorithm. Based on the assumption that the}
          \KeywordTok{corruption} \NormalTok{of the low frequency bias field can be modeled as a convolution of}
          \KeywordTok{the} \NormalTok{intensity histogram by a Gaussian, the basic algorithmic protocol is to}
          \KeywordTok{iterate} \NormalTok{between deconvolving the intensity histogram by a Gaussian, remapping}
          \KeywordTok{the} \NormalTok{intensities, and then spatially smoothing this result by a B-spline modeling}
          \KeywordTok{of} \NormalTok{the bias field itself. The modifications from and improvements obtained over}
          \KeywordTok{the} \NormalTok{original N3 algorithm are described in the following paper: N. Tustison et}
          \KeywordTok{al.}\NormalTok{, N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,}
          \KeywordTok{29}\NormalTok{(6):}\KeywordTok{1310-1320}\NormalTok{, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, N4 tries to infer the dimensionality from the input image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for bias correction. Since N4 log transforms}
          \KeywordTok{the} \NormalTok{intensities, negative values or values close to zero should be processed}
          \KeywordTok{prior} \NormalTok{to correction.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, the final bias correction is only performed in the}
          \KeywordTok{mask} \NormalTok{region. If a weight image is not specified, only intensity values inside}
          \KeywordTok{the} \NormalTok{masked region are used during the execution of the algorithm. If a weight}
          \KeywordTok{image} \NormalTok{is specified, only the non-zero weights are used in the execution of the}
          \KeywordTok{algorithm} \NormalTok{although the mask region defines where bias correction is performed in}
          \KeywordTok{the} \NormalTok{final output. Otherwise bias correction occurs over the entire image domain.}
          \KeywordTok{See} \NormalTok{also the option description for the weight image.}

     \KeywordTok{-r}\NormalTok{, --rescale-intensities 0/(1)}
          \KeywordTok{At} \NormalTok{each iteration, a new intensity mapping is calculated and applied but there}
          \KeywordTok{is} \NormalTok{nothing which constrains the new intensity range to be within certain values.}
          \KeywordTok{The} \NormalTok{result is that the range can }\StringTok{"drift"} \NormalTok{from the original at each iteration.}
          \KeywordTok{This} \NormalTok{option rescales to the [min,max] range of the original image intensities}
          \KeywordTok{within} \NormalTok{the user-specified mask.}

     \KeywordTok{-w}\NormalTok{, --weight-image weightImageFilename}
          \KeywordTok{The} \NormalTok{weight image allows the user to perform a relative weighting of specific}
          \KeywordTok{voxels} \NormalTok{during the B-spline fitting. For example, some studies have shown that N3}
          \KeywordTok{performed} \NormalTok{on white matter segmentations improves performance. If one has a}
          \KeywordTok{spatial} \NormalTok{probability map of the white matter, one can use this map to weight the}
          \KeywordTok{b-spline} \NormalTok{fitting towards those voxels which are more probabilistically}
          \KeywordTok{classified} \NormalTok{as white matter. See also the option description for the mask image.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor 1/2/3/4/...}
          \KeywordTok{Running} \NormalTok{N4 on large images can be time consuming. To lessen computation time,}
          \KeywordTok{the} \NormalTok{input image can be resampled. The shrink factor, specified as a single}
          \KeywordTok{integer}\NormalTok{, describes this resampling. Shrink factors }\KeywordTok{<}\NormalTok{= 4 are commonly used.}

     \KeywordTok{-c}\NormalTok{, --convergence [}\KeywordTok{<}\NormalTok{numberOfIterations=50x50x50x}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{convergenceThreshold=0.}\KeywordTok{0>}\NormalTok{]}
          \KeywordTok{Convergence} \NormalTok{is determined by calculating the coefficient of variation between}
          \KeywordTok{subsequent} \NormalTok{iterations. When this value is less than the specified threshold from}
          \KeywordTok{the} \NormalTok{previous iteration or the maximum number of iterations is exceeded the}
          \KeywordTok{program} \NormalTok{terminates. Multiple resolutions can be specified by using }\StringTok{'x'} \NormalTok{between}
          \KeywordTok{the} \NormalTok{number of iterations at each resolution, e.g. 100x50x50.}

     \KeywordTok{-b}\NormalTok{, --bspline-fitting [splineDistance,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
                           \NormalTok{[}\KeywordTok{initialMeshResolution}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
          \KeywordTok{These} \NormalTok{options describe the b-spline fitting parameters. The initial b-spline}
          \KeywordTok{mesh} \NormalTok{at the coarsest resolution is specified either as the number of elements in}
          \KeywordTok{each} \NormalTok{dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single}
          \KeywordTok{scalar} \NormalTok{parameter which describes the isotropic sizing of the mesh elements. The}
          \KeywordTok{latter} \NormalTok{option is typically preferred. For each subsequent level, the spline}
          \KeywordTok{distance} \NormalTok{decreases in half, or equivalently, the number of mesh elements doubles}
          \KeywordTok{Cubic} \NormalTok{splines (order = 3) }\KeywordTok{are} \NormalTok{typically used.}

     \KeywordTok{-t}\NormalTok{, --histogram-sharpening [}\KeywordTok{<}\NormalTok{FWHM=0.}\KeywordTok{15>}\NormalTok{,}\KeywordTok{<}\NormalTok{wienerNoise=0.}\KeywordTok{01>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfHistogramBins=}\KeywordTok{200>}\NormalTok{]}
          \KeywordTok{These} \NormalTok{options describe the histogram sharpening parameters, i.e. the}
          \KeywordTok{deconvolution} \NormalTok{step parameters described in the original N3 algorithm. The}
          \KeywordTok{default} \NormalTok{values have been shown to work fairly well.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{biasField}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the bias corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated bias field.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\textless{}-- \#\# Atropos -- cutting the threads of fate

\includegraphics{./papers/figures/Atropos_deGoya.jpg} --\textgreater{}

@@

\begin{frame}[fragile]{\texttt{Atropos}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{Atropos} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{Atropos}
          \KeywordTok{A} \NormalTok{finite mixture modeling (FMM) }\KeywordTok{segmentation} \NormalTok{approach with possibilities for}
          \KeywordTok{specifying} \NormalTok{prior constraints. These prior constraints include the specification}
          \KeywordTok{of} \NormalTok{a prior label image, prior probability images (one for each class), }\KeywordTok{and/or} \NormalTok{an}
          \KeywordTok{MRF} \NormalTok{prior to enforce spatial smoothing of the labels. Similar algorithms include}
          \KeywordTok{FAST} \NormalTok{and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open}
          \KeywordTok{source} \NormalTok{multivariate framework for n-tissue segmentation with evaluation on}
          \KeywordTok{public} \NormalTok{data. Neuroinformatics. 2011 Dec}\KeywordTok{;9}\NormalTok{(4):}\KeywordTok{381-400.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, Atropos tries to infer the dimensionality from the first input}
          \KeywordTok{image.}

     \KeywordTok{-a}\NormalTok{, --intensity-image [intensityImage,}\KeywordTok{<}\NormalTok{adaptiveSmoothingWeight}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{One} \NormalTok{or more scalar images is specified for segmentation using the}
          \KeywordTok{-a/--intensity-image} \NormalTok{option. For segmentation scenarios with no prior}
          \KeywordTok{information}\NormalTok{, the first scalar image encountered on the command line is used to}
          \KeywordTok{order} \NormalTok{labelings such that the class with the smallest intensity signature is}
          \KeywordTok{class} \StringTok{'1'} \NormalTok{through class }\StringTok{'N'} \NormalTok{which represents the voxels with the largest}
          \KeywordTok{intensity} \NormalTok{values. The optional adaptive smoothing weight parameter is applicable}
          \KeywordTok{only} \NormalTok{when using prior label or probability images. This scalar parameter is to}
          \KeywordTok{be} \NormalTok{specified between [0,1] which smooths each labeled region separately and}
          \KeywordTok{modulates} \NormalTok{the intensity measurement at each voxel in each intensity image}
          \KeywordTok{between} \NormalTok{the original intensity and its smoothed counterpart. The smoothness}
          \KeywordTok{parameters} \NormalTok{are governed by the -b/--bspline option.}

     \KeywordTok{-b}\NormalTok{, --bspline [}\KeywordTok{<}\NormalTok{numberOfLevels=}\KeywordTok{6>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialMeshResolution=1x1x...}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
          \KeywordTok{If} \NormalTok{the adaptive smoothing weights are }\KeywordTok{>} \NormalTok{0, the intensity images are smoothed in}
          \KeywordTok{calculating} \NormalTok{the likelihood values. This is to account for subtle intensity}
          \KeywordTok{differences} \NormalTok{across the same tissue regions.}

     \KeywordTok{-i}\NormalTok{, --initialization Random[numberOfClasses]}
                          \KeywordTok{Otsu}\NormalTok{[numberOfTissueClasses]}
                          \KeywordTok{KMeans}\NormalTok{[numberOfTissueClasses,}\KeywordTok{<}\NormalTok{clusterCenters(in ascending order and for first intensity image only)}\KeywordTok{>}\NormalTok{]}
                          \KeywordTok{PriorProbabilityImages}\NormalTok{[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) }\KeywordTok{or} \NormalTok{vectorImage,priorWeighting,}\KeywordTok{<}\NormalTok{priorProbabilityThreshold}\KeywordTok{>}\NormalTok{]}
                          \KeywordTok{PriorLabelImage}\NormalTok{[numberOfTissueClasses,labelImage,priorWeighting]}
          \KeywordTok{To} \NormalTok{initialize the FMM parameters, one of the following options must be}
          \KeywordTok{specified.} \NormalTok{If one does not have prior label or probability images we recommend}
          \KeywordTok{using} \NormalTok{kmeans as it is typically faster than otsu and can be used with}
          \KeywordTok{multivariate} \NormalTok{initialization. However, since a Euclidean distance on the inter}
          \KeywordTok{cluster} \NormalTok{distances is used, one might have to appropriately scale the additional}
          \KeywordTok{input} \NormalTok{images. Random initialization is meant purely for intellectual curiosity.}
          \KeywordTok{The} \NormalTok{prior weighting (specified in the range [0,1]) }\KeywordTok{is} \NormalTok{used to modulate the}
          \KeywordTok{calculation} \NormalTok{of the posterior probabilities between the likelihood*mrfprior and}
          \KeywordTok{the} \NormalTok{likelihood*mrfprior*prior. For specifying many prior probability images for}
          \KeywordTok{a} \NormalTok{multi-label segmentation, we offer a minimize usage option (see -m)}\KeywordTok{.} \KeywordTok{With} \NormalTok{that}
          \KeywordTok{option} \NormalTok{one can specify a prior probability threshold in which only those pixels}
          \KeywordTok{exceeding} \NormalTok{that threshold are stored in memory.}

     \KeywordTok{-s}\NormalTok{, --partial-volume-label-set label1xlabel2xlabel3}
          \KeywordTok{The} \NormalTok{partial volume estimation option allows one to modelmixtures of classes}
          \KeywordTok{within} \NormalTok{single voxels. Atropos currently allows the user to model two class}
          \KeywordTok{mixtures} \NormalTok{per partial volume class. The user specifies a set of class labels per}
          \KeywordTok{partial} \NormalTok{volume class requested. For example, suppose the user was performing a}
          \KeywordTok{classic} \NormalTok{3-tissue segmentation (csf, gm, wm) }\KeywordTok{using} \NormalTok{kmeans initialization. Suppose}
          \KeywordTok{the} \NormalTok{user also wanted to model the partial voluming effects between csf/gm and}
          \KeywordTok{gm/wm.} \NormalTok{The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for}
          \KeywordTok{this} \NormalTok{example, there would be 3 tissue classes and 2 partial volume classes.}
          \KeywordTok{Optionally}\NormalTok{,the user can limit partial volume handling to mrf considerations only}
          \KeywordTok{whereby} \NormalTok{the output would only be the three tissues.}

     \KeywordTok{--use-partial-volume-likelihoods} \NormalTok{1/(0)}
                                      \KeywordTok{true}\NormalTok{/}\KeywordTok{(false)}
          \KeywordTok{The} \NormalTok{user can specify whether or not to use the partial volume likelihoods, in}
          \KeywordTok{which} \NormalTok{case the partial volume class is considered separate from the tissue}
          \KeywordTok{classes.} \NormalTok{Alternatively, one can use the MRF only to handle partial volume in}
          \KeywordTok{which} \NormalTok{case, partial volume voxels are not considered as separate classes.}

     \KeywordTok{-p}\NormalTok{, --posterior-formulation Socrates[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Plato}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Aristotle}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Sigmoid}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]]}
          \KeywordTok{Different} \NormalTok{posterior probability formulations are possible as are different}
          \KeywordTok{update} \NormalTok{options. To guarantee theoretical convergence properties, a proper}
          \KeywordTok{formulation} \NormalTok{of the well-known iterated conditional modes (ICM) }\KeywordTok{uses} \NormalTok{an}
          \KeywordTok{asynchronous} \NormalTok{update step modulated by a specified annealing temperature. If one}
          \KeywordTok{sets} \NormalTok{the AnnealingTemperature }\KeywordTok{>} \NormalTok{1 in the posterior formulation a traditional}
          \KeywordTok{code} \NormalTok{set for a proper ICM update will be created. Otherwise, a synchronous}
          \KeywordTok{update} \NormalTok{step will take place at each iteration. The annealing temperature, T,}
          \KeywordTok{converts} \NormalTok{the posteriorProbability to posteriorProbability^(1/T) }\KeywordTok{over} \NormalTok{the course}
          \KeywordTok{of} \NormalTok{optimization.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{The} \NormalTok{image mask (which is required) }\KeywordTok{defines} \NormalTok{the region which is to be labeled by}
          \KeywordTok{the} \NormalTok{Atropos algorithm.}

     \KeywordTok{-c}\NormalTok{, --convergence numberOfIterations}
                       \NormalTok{[}\KeywordTok{<}\OtherTok{numberOfIterations=}\NormalTok{5}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\OtherTok{convergenceThreshold=}\NormalTok{0.001}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Convergence} \NormalTok{is determined by calculating the mean maximum posterior probability}
          \KeywordTok{over} \NormalTok{the region of interest at each iteration. When this value decreases or}
          \KeywordTok{increases} \NormalTok{less than the specified threshold from the previous iteration or the}
          \KeywordTok{maximum} \NormalTok{number of iterations is exceeded the program terminates.}

     \KeywordTok{-k}\NormalTok{, --likelihood-model Gaussian}
                            \KeywordTok{HistogramParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{sigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfBins=}\KeywordTok{32>}\NormalTok{]}
                            \KeywordTok{ManifoldParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{pointSetSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{evaluationKNeighborhood=}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{CovarianceKNeighborhood=}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{kernelSigma=}\KeywordTok{0>}\NormalTok{]}
                            \KeywordTok{JointShapeAndOrientationProbability}\NormalTok{[}\KeywordTok{<}\NormalTok{shapeSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfShapeBins=}\KeywordTok{64>}\NormalTok{, }\KeywordTok{<}\NormalTok{orientationSigma=1.}\KeywordTok{0>}\NormalTok{, }\KeywordTok{<}\NormalTok{numberOfOrientationBins=}\KeywordTok{32>}\NormalTok{]}
                            \KeywordTok{LogEuclideanGaussian}
          \KeywordTok{Both} \NormalTok{parametric and non-parametric options exist in Atropos. The Gaussian}
          \KeywordTok{parametric} \NormalTok{option is commonly used (e.g. SPM }\KeywordTok{&} \KeywordTok{FAST}\NormalTok{) }\KeywordTok{where} \NormalTok{the mean and standard}
          \KeywordTok{deviation} \NormalTok{for the Gaussian of each class is calculated at each iteration. Other}
          \KeywordTok{groups} \NormalTok{use non-parametric approaches exemplified by option 2. We recommend using}
          \KeywordTok{options} \NormalTok{1 or 2 as they are fairly standard and the default parameters work}
          \KeywordTok{adequately.}

     \KeywordTok{-m}\NormalTok{, --mrf [}\KeywordTok{<}\NormalTok{smoothingFactor=0.}\KeywordTok{3>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
               \NormalTok{[}\KeywordTok{<mrfCoefficientImage>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Markov} \NormalTok{random field (MRF) }\KeywordTok{theory} \NormalTok{provides a general framework for enforcing}
          \KeywordTok{spatially} \NormalTok{contextual constraints on the segmentation solution. The default}
          \KeywordTok{smoothing} \NormalTok{factor of 0.3 provides a moderate amount of smoothing. Increasing this}
          \KeywordTok{number} \NormalTok{causes more smoothing whereas decreasing the number lessens the}
          \KeywordTok{smoothing.} \NormalTok{The radius parameter specifies the mrf neighborhood. Different update}
          \KeywordTok{schemes} \NormalTok{are possible but only the asynchronous updating has theoretical}
          \KeywordTok{convergence} \NormalTok{properties.}

     \KeywordTok{-g}\NormalTok{, --icm [}\KeywordTok{<}\NormalTok{useAsynchronousUpdate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{maximumNumberOfICMIterations=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{icmCodeImage=}\StringTok{''}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Asynchronous} \NormalTok{updating requires the construction of an ICM code image which is a}
          \KeywordTok{label} \NormalTok{image (with labels in the range }\DataTypeTok{\{1,..,MaximumICMCode\}}\NormalTok{) }\KeywordTok{constructed} \NormalTok{such}
          \KeywordTok{that} \NormalTok{no MRF neighborhood has duplicate ICM code labels. Thus, to update the}
          \KeywordTok{voxel} \NormalTok{class labels we iterate through the code labels and, for each code label,}
          \KeywordTok{we} \NormalTok{iterate through the image and update the voxel class label that has the}
          \KeywordTok{corresponding} \NormalTok{ICM code label. One can print out the ICM code image by specifying}
          \KeywordTok{an} \NormalTok{ITK-compatible image filename.}

     \KeywordTok{-r}\NormalTok{, --use-random-seed 0/(1)}
          \KeywordTok{Initialize} \NormalTok{internal random number generator with a random seed. Otherwise,}
          \KeywordTok{initialize} \NormalTok{with a constant seed number.}

     \KeywordTok{-o}\NormalTok{, --output [classifiedImage,}\KeywordTok{<}\NormalTok{posteriorProbabilityImageFileNameFormat}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of a labeled image where each voxel in the masked region is}
          \KeywordTok{assigned} \NormalTok{a label from 1, 2, ..., N. Optionally, one can also output the}
          \KeywordTok{posterior} \NormalTok{probability images specified in the same format as the prior}
          \KeywordTok{probability} \NormalTok{images, e.g. posterior%02d.nii.gz (C-style file name formatting)}\KeywordTok{.}

     \KeywordTok{-u}\NormalTok{, --minimize-memory-usage (0)}\KeywordTok{/1}
          \KeywordTok{By} \NormalTok{default, memory usage is not minimized, however, if this is needed, the}
          \KeywordTok{various} \NormalTok{probability and distance images are calculated on the fly instead of}
          \KeywordTok{being} \NormalTok{stored in memory at each iteration. Also, if prior probability images are}
          \KeywordTok{used}\NormalTok{, only the non-negligible pixel values are stored in memory.}
          \KeywordTok{<VALUES>}\NormalTok{: 0}

     \KeywordTok{-w}\NormalTok{, --winsorize-outliers BoxPlot[}\KeywordTok{<}\NormalTok{lowerPercentile=0.}\KeywordTok{25>}\NormalTok{,}\KeywordTok{<}\NormalTok{upperPercentile=0.}\KeywordTok{75>}\NormalTok{,}\KeywordTok{<}\NormalTok{whiskerLength=1.}\KeywordTok{5>}\NormalTok{]}
                              \KeywordTok{GrubbsRosner}\NormalTok{[}\KeywordTok{<}\NormalTok{significanceLevel=0.}\KeywordTok{05>}\NormalTok{,}\KeywordTok{<}\NormalTok{winsorizingLevel=0.}\KeywordTok{10>}\NormalTok{]}
          \KeywordTok{To} \NormalTok{remove the effects of outliers in calculating the weighted mean and weighted}
          \KeywordTok{covariance}\NormalTok{, the user can opt to remove the outliers through the options}
          \KeywordTok{specified} \NormalTok{below.}

>>>>

\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}

\begin{itemize}
\item
  Developed at the Montreal Neurological Institute (John Sled, 1998)
\item
  Part of the standard preprocessing protocol in large scale projects
  such as ADNI
\item
  The traditional de facto standard in MRI bias correction

  \begin{itemize}
  \tightlist
  \item
    good performance
  \item
    \emph{public availability}
  \end{itemize}
\item
  Public availability --- set of perl scripts coordinating various C++
  programs
\item
  ``\emph{Let's incorporate N3 into ANTs!}''
\end{itemize}

@@

@@

\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}

\includegraphics{./tools/atropos/figures/atroposFlow.png}
